### 2025-07-20 evaluating-prediction-accuracy.qmd
20250719 - accuracy of crowd-averaged projections

projectionsWithActuals_seasonal_db <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "DB")
```

@@

projectionsWithActuals_weekly_db <- projectionsWithActuals_weekly %>% 
  filter(position_group == "DB")
```

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

projectionsWithActuals_seasonal_db <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "DB")

crowdAveragedProjectionsWithActuals_seasonal_qb <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(position_group == "QB")

crowdAveragedProjectionsWithActuals_seasonal_rb <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(position_group == "RB")

crowdAveragedProjectionsWithActuals_seasonal_wr <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(position_group == "WR")

crowdAveragedProjectionsWithActuals_seasonal_te <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(position_group == "TE")

crowdAveragedProjectionsWithActuals_seasonal_k <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(position == "K")

crowdAveragedProjectionsWithActuals_seasonal_dl <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(position_group == "DL")

crowdAveragedProjectionsWithActuals_seasonal_lb <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(position_group == "LB")

crowdAveragedProjectionsWithActuals_seasonal_db <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(position_group == "DB")
```

@@

projectionsWithActuals_weekly_db <- projectionsWithActuals_weekly %>% 
  filter(position_group == "DB")

crowdAveragedProjectionsWithActuals_weekly_qb <- crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(position_group == "QB")

crowdAveragedProjectionsWithActuals_weekly_rb <- crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(position_group == "RB")

crowdAveragedProjectionsWithActuals_weekly_wr <- crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(position_group == "WR")

crowdAveragedProjectionsWithActuals_weekly_te <- crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(position_group == "TE")

crowdAveragedProjectionsWithActuals_weekly_k <- crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(position == "K")

crowdAveragedProjectionsWithActuals_weekly_dl <- crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(position_group == "DL")

crowdAveragedProjectionsWithActuals_weekly_lb <- crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(position_group == "LB")

crowdAveragedProjectionsWithActuals_weekly_db <- crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(position_group == "DB")
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections of all players (across all positions):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_overall_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_overall_crowd <- round(accuracyIndices_seasonal_overall_crowd$rsquared, digits = 2)
me_seasonal_overall_crowd <- round(accuracyIndices_seasonal_overall_crowd$ME, digits = 2)
mae_seasonal_overall_crowd <- round(accuracyIndices_seasonal_overall_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of players across all positions, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal$points[which(crowdAveragedProjectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_overall_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal$points[which(crowdAveragedProjectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_overall_crowd_subset <- round(accuracyIndices_seasonal_overall_crowd_subset$rsquared, digits = 2)
me_seasonal_overall_crowd_subset <- round(accuracyIndices_seasonal_overall_crowd_subset$ME, digits = 2)
mae_seasonal_overall_crowd_subset <- round(accuracyIndices_seasonal_overall_crowd_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections for Quarterbacks:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_qb$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_qb$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_qb_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_qb$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_qb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_qb_crowd <- round(accuracyIndices_seasonal_qb_crowd$rsquared, digits = 2)
me_seasonal_qb_crowd <- round(accuracyIndices_seasonal_qb_crowd$ME, digits = 2)
mae_seasonal_qb_crowd <- round(accuracyIndices_seasonal_qb_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of Quarterbacks, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_qb$points[which(crowdAveragedProjectionsWithActuals_seasonal_qb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_qb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_qb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_qb_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_qb$points[which(crowdAveragedProjectionsWithActuals_seasonal_qb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_qb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_qb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_qb_crowd_subset <- round(accuracyIndices_seasonal_qb_crowd_subset$rsquared, digits = 2)
me_seasonal_qb_crowd_subset <- round(accuracyIndices_seasonal_qb_crowd_subset$ME, digits = 2)
mae_seasonal_qb_crowd_subset <- round(accuracyIndices_seasonal_qb_crowd_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections for Running Backs:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_rb$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_rb$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_rb_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_rb$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_rb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_rb_crowd <- round(accuracyIndices_seasonal_rb_crowd$rsquared, digits = 2)
me_seasonal_rb_crowd <- round(accuracyIndices_seasonal_rb_crowd$ME, digits = 2)
mae_seasonal_rb_crowd <- round(accuracyIndices_seasonal_rb_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of Running Backs, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_rb$points[which(crowdAveragedProjectionsWithActuals_seasonal_rb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_rb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_rb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_rb_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_rb$points[which(crowdAveragedProjectionsWithActuals_seasonal_rb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_rb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_rb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_rb_crowd_subset <- round(accuracyIndices_seasonal_rb_crowd_subset$rsquared, digits = 2)
me_seasonal_rb_crowd_subset <- round(accuracyIndices_seasonal_rb_crowd_subset$ME, digits = 2)
mae_seasonal_rb_crowd_subset <- round(accuracyIndices_seasonal_rb_crowd_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections for Wide Receivers:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_wr$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_wr$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_wr_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_wr$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_wr$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_wr_crowd <- round(accuracyIndices_seasonal_wr_crowd$rsquared, digits = 2)
me_seasonal_wr_crowd <- round(accuracyIndices_seasonal_wr_crowd$ME, digits = 2)
mae_seasonal_wr_crowd <- round(accuracyIndices_seasonal_wr_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of Wide Receivers, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_wr$points[which(crowdAveragedProjectionsWithActuals_seasonal_wr$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_wr$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_wr$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_wr_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_wr$points[which(crowdAveragedProjectionsWithActuals_seasonal_wr$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_wr$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_wr$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_wr_crowd_subset <- round(accuracyIndices_seasonal_wr_crowd_subset$rsquared, digits = 2)
me_seasonal_wr_crowd_subset <- round(accuracyIndices_seasonal_wr_crowd_subset$ME, digits = 2)
mae_seasonal_wr_crowd_subset <- round(accuracyIndices_seasonal_wr_crowd_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections for Tight Ends:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_te$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_te$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_te_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_te$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_te$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_te_crowd <- round(accuracyIndices_seasonal_te_crowd$rsquared, digits = 2)
me_seasonal_te_crowd <- round(accuracyIndices_seasonal_te_crowd$ME, digits = 2)
mae_seasonal_te_crowd <- round(accuracyIndices_seasonal_te_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of Tight Ends, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_te$points[which(crowdAveragedProjectionsWithActuals_seasonal_te$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_te$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_te$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_te_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_te$points[which(crowdAveragedProjectionsWithActuals_seasonal_te$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_te$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_te$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_te_crowd_subset <- round(accuracyIndices_seasonal_te_crowd_subset$rsquared, digits = 2)
me_seasonal_te_crowd_subset <- round(accuracyIndices_seasonal_te_crowd_subset$ME, digits = 2)
mae_seasonal_te_crowd_subset <- round(accuracyIndices_seasonal_te_crowd_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections for Kickers:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_k$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_k$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_k_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_k$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_k$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_k_crowd <- round(accuracyIndices_seasonal_k_crowd$rsquared, digits = 2)
me_seasonal_k_crowd <- round(accuracyIndices_seasonal_k_crowd$ME, digits = 2)
mae_seasonal_k_crowd <- round(accuracyIndices_seasonal_k_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of Kickers, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_k$points[which(crowdAveragedProjectionsWithActuals_seasonal_k$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_k$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_k$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_k_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_k$points[which(crowdAveragedProjectionsWithActuals_seasonal_k$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_k$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_k$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_k_crowd_subset <- round(accuracyIndices_seasonal_k_crowd_subset$rsquared, digits = 2)
me_seasonal_k_crowd_subset <- round(accuracyIndices_seasonal_k_crowd_subset$ME, digits = 2)
mae_seasonal_k_crowd_subset <- round(accuracyIndices_seasonal_k_crowd_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections for Defensive Linemen:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_dl$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_dl$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_dl_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_dl$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_dl$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_dl_crowd <- round(accuracyIndices_seasonal_dl_crowd$rsquared, digits = 2)
me_seasonal_dl_crowd <- round(accuracyIndices_seasonal_dl_crowd$ME, digits = 2)
mae_seasonal_dl_crowd <- round(accuracyIndices_seasonal_dl_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of Defensive Linemen, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_dl$points[which(crowdAveragedProjectionsWithActuals_seasonal_dl$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_dl$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_dl$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_dl_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_dl$points[which(crowdAveragedProjectionsWithActuals_seasonal_dl$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_dl$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_dl$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_dl_crowd_subset <- round(accuracyIndices_seasonal_dl_crowd_subset$rsquared, digits = 2)
me_seasonal_dl_crowd_subset <- round(accuracyIndices_seasonal_dl_crowd_subset$ME, digits = 2)
mae_seasonal_dl_crowd_subset <- round(accuracyIndices_seasonal_dl_crowd_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections for Linebackers:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_lb$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_lb$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_lb_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_lb$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_lb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_lb_crowd <- round(accuracyIndices_seasonal_lb_crowd$rsquared, digits = 2)
me_seasonal_lb_crowd <- round(accuracyIndices_seasonal_lb_crowd$ME, digits = 2)
mae_seasonal_lb_crowd <- round(accuracyIndices_seasonal_lb_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of Linebackers, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_lb$points[which(crowdAveragedProjectionsWithActuals_seasonal_lb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_lb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_lb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_lb_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_lb$points[which(crowdAveragedProjectionsWithActuals_seasonal_lb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_lb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_lb$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_lb_crowd_subset <- round(accuracyIndices_seasonal_lb_crowd_subset$rsquared, digits = 2)
me_seasonal_lb_crowd_subset <- round(accuracyIndices_seasonal_lb_crowd_subset$ME, digits = 2)
mae_seasonal_lb_crowd_subset <- round(accuracyIndices_seasonal_lb_crowd_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for crowd-averaged projections for Defensive Backs:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_db$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_db$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_db_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_db$points,
  actual = crowdAveragedProjectionsWithActuals_seasonal_db$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_db_crowd <- round(accuracyIndices_seasonal_db_crowd$rsquared, digits = 2)
me_seasonal_db_crowd <- round(accuracyIndices_seasonal_db_crowd$ME, digits = 2)
mae_seasonal_db_crowd <- round(accuracyIndices_seasonal_db_crowd$MAE, digits = 2)
```

Here are the seasonal accuracy indexes for crowd-averaged projections of Defensive Backs, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_db$points[which(crowdAveragedProjectionsWithActuals_seasonal_db$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_db$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_db$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

accuracyIndices_seasonal_db_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_seasonal_db$points[which(crowdAveragedProjectionsWithActuals_seasonal_db$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = crowdAveragedProjectionsWithActuals_seasonal_db$fantasyPoints[which(crowdAveragedProjectionsWithActuals_seasonal_db$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_db_crowd_subset <- round(accuracyIndices_seasonal_db_crowd_subset$rsquared, digits = 2)
me_seasonal_db_crowd_subset <- round(accuracyIndices_seasonal_db_crowd_subset$ME, digits = 2)
mae_seasonal_db_crowd_subset <- round(accuracyIndices_seasonal_db_crowd_subset$MAE, digits = 2)
```

@@

Here are the weekly accuracy indexes for crowd-averaged projections of all players (across all positions):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly$points,
  actual = crowdAveragedProjectionsWithActuals_weekly$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_weekly_overall_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly$points,
  actual = crowdAveragedProjectionsWithActuals_weekly$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_overall_crowd <- round(accuracyIndices_weekly_overall_crowd$rsquared, digits = 2)
me_weekly_overall_crowd <- round(accuracyIndices_weekly_overall_crowd$ME, digits = 2)
mae_weekly_overall_crowd <- round(accuracyIndices_weekly_overall_crowd$MAE, digits = 2)
```

Here are the weekly accuracy indexes for crowd-averaged projections of players across all positions, but only among those who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly$points[which(crowdAveragedProjectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = crowdAveragedProjectionsWithActuals_weekly$fantasyPoints[which(crowdAveragedProjectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

accuracyIndices_weekly_overall_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly$points[which(crowdAveragedProjectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = crowdAveragedProjectionsWithActuals_weekly$fantasyPoints[which(crowdAveragedProjectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_overall_crowd_subset <- round(accuracyIndices_weekly_overall_crowd_subset$rsquared, digits = 2)
me_weekly_overall_crowd_subset <- round(accuracyIndices_weekly_overall_crowd_subset$ME, digits = 2)
mae_weekly_overall_crowd_subset <- round(accuracyIndices_weekly_overall_crowd_subset$MAE, digits = 2)
```

@@

Here are the weekly accuracy indexes for crowd-averaged projections of Quarterbacks:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_qb$points,
  actual = crowdAveragedProjectionsWithActuals_weekly_qb$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_weekly_qb_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_qb$points,
  actual = crowdAveragedProjectionsWithActuals_weekly_qb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_qb_crowd <- round(accuracyIndices_weekly_qb_crowd$rsquared, digits = 2)
me_weekly_qb_crowd <- round(accuracyIndices_weekly_qb_crowd$ME, digits = 2)
mae_weekly_qb_crowd <- round(accuracyIndices_weekly_qb_crowd$MAE, digits = 2)
```

Here are the weekly accuracy indexes for crowd-averaged projections of Quarterbacks, but only among those who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_qb$points[which(crowdAveragedProjectionsWithActuals_weekly_qb$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = crowdAveragedProjectionsWithActuals_weekly_qb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_weekly_qb$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

accuracyIndices_weekly_qb_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_qb$points[which(crowdAveragedProjectionsWithActuals_weekly_qb$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = crowdAveragedProjectionsWithActuals_weekly_qb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_weekly_qb$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_qb_crowd_subset <- round(accuracyIndices_weekly_qb_crowd_subset$rsquared, digits = 2)
me_weekly_qb_crowd_subset <- round(accuracyIndices_weekly_qb_crowd_subset$ME, digits = 2)
mae_weekly_qb_crowd_subset <- round(accuracyIndices_weekly_qb_crowd_subset$MAE, digits = 2)
```

@@

Here are the weekly accuracy indexes for crowd-averaged projections of Running Backs:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_rb$points,
  actual = crowdAveragedProjectionsWithActuals_weekly_rb$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_weekly_rb_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_rb$points,
  actual = crowdAveragedProjectionsWithActuals_weekly_rb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_rb_crowd <- round(accuracyIndices_weekly_rb_crowd$rsquared, digits = 2)
me_weekly_rb_crowd <- round(accuracyIndices_weekly_rb_crowd$ME, digits = 2)
mae_weekly_rb_crowd <- round(accuracyIndices_weekly_rb_crowd$MAE, digits = 2)
```

Here are the weekly accuracy indexes for crowd-averaged projections of Running Backs, but only among those who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_rb$points[which(crowdAveragedProjectionsWithActuals_weekly_rb$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = crowdAveragedProjectionsWithActuals_weekly_rb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_weekly_rb$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

accuracyIndices_weekly_rb_crowd_subset <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_rb$points[which(crowdAveragedProjectionsWithActuals_weekly_rb$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = crowdAveragedProjectionsWithActuals_weekly_rb$fantasyPoints[which(crowdAveragedProjectionsWithActuals_weekly_rb$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_rb_crowd_subset <- round(accuracyIndices_weekly_rb_crowd_subset$rsquared, digits = 2)
me_weekly_rb_crowd_subset <- round(accuracyIndices_weekly_rb_crowd_subset$ME, digits = 2)
mae_weekly_rb_crowd_subset <- round(accuracyIndices_weekly_rb_crowd_subset$MAE, digits = 2)
```

@@

Here are the weekly accuracy indexes for crowd-averaged projections of Wide Receivers:

```{r}
petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_wr$points,
  actual = crowdAveragedProjectionsWithActuals_weekly_wr$fantasyPoints,
  dropUndefined = TRUE
)
```

accuracyIndices_weekly_wr_crowd <- petersenlab::accuracyOverall(
  predicted = crowdAveragedProjectionsWithActuals_weekly_wr$points,
  actual = crowdAveragedProjectionsWithActuals_weekly_wr$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_wr_crowd <- round(accuracyIndices_weekly_wr_crowd$rsquared, digits = 2)
me_weekly_wr_crowd <- round(accuracyIndices_weekly_wr_crowd$ME, digits = 2)
mae_weekly_wr_crowd <- round(accuracyIndices_weekly_wr_crowd$MAE, digits = 2)
```
